---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

# Report Details

```{r}
articleID <- 6-7-2014 
reportType <- 'copilot' 
pilotNames <- 'Effie Li' 
copilotNames <- 'Ayo Dada' 
pilotTTC <- 180 
copilotTTC <- 120 
pilotStartDate <- '11/09/19' 
copilotStartDate <- '11/10/19' 
completionDate <- '11/10/19' 
```

------

#### Methods summary: 

This study recruited participants from either the eastbound platform or the westbound platform of the Bay Street station in Toronto. Participants each rated how far one of the four stations -- (from west to east) Spadina station, the St. George station, the Bloor-Yonge station, or the Sherbourne station -- felt using a scale from 1 to 7.

------

#### Target outcomes: 

We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20. We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations. Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28) and the station two stops to the west (Spadina, p = .001, ηp2 = .20). The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08) and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24). Figure 1 summarizes these results. comparing

------

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(lsr) # For the computation of ANOVAs in R
```

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
data = read_excel('GroupB_6-7-2014/data/S1_Subway.xlsx')
```

# Step 3: Tidy data

This dataset was already in the tidy form.

# Step 4: Run analysis

## Pre-processing
The original paper did not specify any necessary pre-processing steps.

## Descriptive statistics
The targeted outcomes do not include descriptive statistics. To help interpret the anova results below, we provide the means and standard deviations of both groups of participants' ratings of distance per station.

```{r}
descriptives <- data %>%
  group_by(DIRECTION, STN_NAME) %>%
  summarize(meanDISTANCE=mean(DISTANCE), stdDISTANCE=sd(DISTANCE))
```

## Inferential statistics

"We carried out a 2 (orientation: toward, away from) × 4 (station: Spadina, St. George, Bloor-Yonge, Sherbourne) analysis of variance (ANOVA) on closeness ratings, which revealed no main effect of orientation, F < 1, and a main effect of station, F(3, 194) = 24.10, p < .001, ηp2 = .27. This main effect was qualified by the predicted interaction between orientation and station, F(3, 194) = 16.28, p < .001, ηp2 = .20."

```{r}
# run two-way ANOVA
fit = aov(DISTANCE ~ DIRECTION*STN_NAME, data = data)
summary(fit)
etaSquared(fit)

# check values (in the order of presentation in the quote above)
# no main effect of orientation (DIRECTION)
reportObject <- reproCheck(reportedValue = '<1', obtainedValue = '0.664', valueType = 'F', eyeballCheck = TRUE)
# main effect of station (STN_NAME)
reportObject <- reproCheck(reportedValue = '3', obtainedValue = '3', valueType = 'df')
reportObject <- reproCheck(reportedValue = '194', obtainedValue = '194', valueType = 'df')
reportObject <- reproCheck(reportedValue = '24.10', obtainedValue = '23.349', valueType = 'F')
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = '6.01e-13', valueType = 'p', eyeballCheck = TRUE)
reportObject <- reproCheck(reportedValue = '.27', obtainedValue = '0.265284110', valueType = 'pes')
# interaction
reportObject <- reproCheck(reportedValue = '16.28', obtainedValue = '16.283', valueType = 'F')
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = '1.77e-09', valueType = 'p', eyeballCheck = TRUE)
reportObject <- reproCheck(reportedValue = '.20', obtainedValue = '0.201151614', valueType = 'pes')
```

“We decomposed this interaction by the subjective-distance ratings between participants traveling east and west for each of the four subway stations.”

```{r}
# split data based on subway stations
BY = data %>% filter(STN_NAME=='B-Y')
sher = data %>% filter(STN_NAME=='SHER')
spad = data %>% filter(STN_NAME=='SPAD')
stg = data %>% filter(STN_NAME=='STG')
```

"Westbound participants rated the stations to the west of Bay Street as closer than did eastbound participants; this effect was obtained for both the station one stop to the west (St. George, p < .001, ηp2 = .28)..."  

St. George:
```{r}
fit_stg = aov(DISTANCE ~ DIRECTION, data = stg)
summary(fit_stg)
etaSquared(fit_stg)

# check values (in the order of presentation in the quote above)
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = '7.23e-05', valueType = 'p', eyeballCheck = TRUE)
reportObject <- reproCheck(reportedValue = '.28', obtainedValue = '0.2772092', valueType = 'pes')
```

"...and the station two stops to the west (Spadina, p = .001, ηp2 = .20)."  

Spadina:
```{r}
fit_spad = aov(DISTANCE ~ DIRECTION, data = spad)
summary(fit_spad)
etaSquared(fit_spad)

# check values (in the order of presentation in the quote above)
reportObject <- reproCheck(reportedValue = '.001', obtainedValue = '0.00113', valueType = 'p')
reportObject <- reproCheck(reportedValue = '.20', obtainedValue = '0.1962763', valueType = 'pes')
```

"The opposite pattern held true for stations to the east of Bay Street. Eastbound participants rated the stations to the east of Bay Street as closer than did westbound participants; this effect was obtained for both the station one stop to the east (Bloor-Yonge, p = .053, ηp2 = .08)..."  

Bloor-Yonge:
```{r}
fit_by = aov(DISTANCE ~ DIRECTION, data = BY)
summary(fit_by)
etaSquared(fit_by)

# check values (in the order of presentation in the quote above)
reportObject <- reproCheck(reportedValue = '.053', obtainedValue = '0.0528', valueType = 'p')
reportObject <- reproCheck(reportedValue = '.08', obtainedValue = '0.0774451', valueType = 'pes')
```

"...and the station two stops to the east (Sherbourne, p < .001, ηp2 = .24)."  

Sherbourne:
```{r}
fit_sher = aov(DISTANCE ~ DIRECTION, data = sher)
summary(fit_sher)
etaSquared(fit_sher)

# check values (in the order of presentation in the quote above)
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = '0.000305', valueType = 'p', eyeballCheck = TRUE)
reportObject <- reproCheck(reportedValue = '.24', obtainedValue = '0.2356667', valueType = 'pes')
```

# Step 5: Conclusion

This reproduction of the original analysis descrived in Study 1 was a success. All the values included in the target outcomes were replicated with matching values, except a minor difference (3% difference) of the F-statistic of the main effect of station in the two-way ANOVA.

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
